\documentclass{dmistyle}
\usepackage{multicol}

\setlength\parindent{0pt}
\setlength\columnseprule{.5pt}
\setlength\columnsep{18pt}
\begin{document}

\section{Hypnosis 101 (pre-EMF)}

\subsection{Welcome}

\begin{itemize}
	\item Bit about me \& mindhackers
	\item Personal intros from everyone:
		\begin{itemize}
			\item Name, member, etc?
			\item How did people find out about hypnosis/course?
			\item What are their interests/reasons?
			\item Any prior experience as hypnotist/subject?
		\end{itemize}
\end{itemize}

\subsection{Introduction}

\begin{multicols}{2}
\begin{itemize}
	\item What hypnosis is and is not
	\item Reassurances
	\item Brief info about the origins
	\item 1952 Hypnotism Act
	\item \textbf{Compare:} clinical/informal/stage hypnosis
	\item NLP \& meditation
	\item Differences between people:
		\begin{itemize}
			\item Depth of trance
			\item Reactions to suggestions
		\end{itemize}
\end{itemize}
\end{multicols}

\subsection{Warnings}

\begin{multicols}{2}
\begin{itemize}
	\item \textbf{Be alert} for \emph{abreactions}
	\item \textbf{Beware} ``taboos''
		\begin{itemize}
			\item Alcohol
			\item Cigarettes
			\item Pork
			\item etc.
		\end{itemize}
	\item \textbf{Never} use potential allergens (e.g.\ tasting peanut butter)
	\item \textbf{\color{blue!50!black}Do not} age-regress
	\item \textbf{\color{blue!50!black}Do not} re-live trauma
	\item \textbf{\color{blue!50!black}Be careful} not to rewrite memories
	\item \textbf{Avoid} embarrassing the subject
	\item \textbf{Remember:} take it seriously
	\item \textbf{Remember:} it's never about the hypnotist
	\item The subject is the one that's important
\end{itemize}
\end{multicols}

\subsection{Practicals}

\subsubsection{Imagination demonstrations}

\begin{multicols}{3}
\begin{itemize}
	\item Hand-clasp lock
	\item Magnetic fingertips
	\item Books and balloons
	\item Backwards force
\end{itemize}
\end{multicols}

\subsection{Signs of hypnosis}

\textbf{\color{red!50!black}No hard rules}

\begin{multicols}{2}
\begin{itemize}
	\item Eyelid flutter
	\item Deep, regular breathing
	\item Muscular relaxation (inc.\ face) \& twitches
	\item Change in skin colour (lighter/flushed)
	\item Reduced movement
	\item Tone of voice changes (slower/lower)
\end{itemize}
\end{multicols}

\subsubsection{Induction types}

Go through the different types, with explanations and demonstrations.

\begin{multicols}{2}
\begin{itemize}
	\item Narrative
	\item Eye fixation
	\item Progressive muscle relaxation
	\item Confusion
	\item ``Instant''
	\item Self-hypnosis
	\item \textbf{Compare:} Direct/indirect
	\item \textbf{Compare:} Physical/verbal/visual
	\item Induction vs.\ deepener
	\item Switching methods
\end{itemize}
\end{multicols}

\subsubsection{Inductions}

\begin{multicols}{3}
\begin{itemize}
	\item Staircase
	\item Even/odd open/close eyes
	\item Clock face
	\item Blackboard
	\item Hand pressure
	\item Handshake interrupt
\end{itemize}
\end{multicols}

\clearpage
\subsection{Hypnotic effects}

Discuss and demonstrate some hypnotic effects. Examples:

\begin{multicols}{3}
\begin{itemize}
	\item Eyelid catalepsy
	\item Arm catalepsy
		\begin{itemize}
			\item Steel bar (hypnotic)
			\item Locked in place (waking)
		\end{itemize}
	\item Stuck to chair
	\item Hot seat
	\item Full relaxation below neck
	\item Cotton wool mouth
	\item Emotional: Happy/giggly
	\item Physiological: Caffeine shot
	\item Memory: forgetting number
	\item Memory: forgetting name?
\end{itemize}
\end{multicols}


\end{document}
